Search-Based Test Data Generation for JavaScript Functions that Interact with the DOM

### 2018-01-30 doc/icse2018/icse2018.tex
Continue working on related work

\usepackage{tablefootnote}
\usepackage{syntax}
\usepackage{multirow}
\usepackage{multicol}
\usepackage{booktabs} % For formal tables
\usepackage{tikz}
\usetikzlibrary{arrows,shadows,positioning,decorations.pathmorphing}
\usepackage{pgf-umlsd}
\usepackage{tikz-uml}
\usepackage{hyperref}
\usepackage{upquote}
\usepackage{listings}
\usepackage{lsthaskell}
\usepackage{xspace}
\usepackage{enumitem}
\usepackage{mdframed}
\usepackage{algorithmic}
\usepackage{longtable}
\usepackage{subcaption}
\usepackage{pgfplots}
\pgfplotsset{compat=newest}
\usepackage[titlenotnumbered, linesnumbered, ruled]{algorithm2e} % language for algorithm description
\hypersetup{
  colorlinks   = true, %Colours links instead of ugly boxes
  urlcolor     = blue, %Colour for external hyperlinks
  linkcolor    = red, %Colour of internal links
  citecolor    = green %Colour of citations
}

@@

TODO: maybe expand this section with the JS type casting for branch distance computation

@@

@@

\section{Discussion}
\label{sec.disc}

\subsection{Future Work}
\label{sub.sec.fut.work}

We would like to open source our test generation framework and introduce a web service allowing developers to submit their JS code for automated testing. One benefit of such service from the perspective of future research is an ability to learn about programming style and the use of JS libraries. Being dynamic language, JS supports various programming styles, which is, as was widely admitted~\cite{paper}, hindrance the complete analysis of JS programs. By gathering feedback about JS programs on which our framework performed poorly, we can identify and prioritize language constructs and programming patterns that should be adequately addressed. Currently, our framework imposes certain explicit constraints on the kind of JS functions it is able to process: 
\begin{enumerate}
\item ability to assign static types to input parameters 
\item no support for the \emph{Object} type, heterogeneous arrays and high-order functions
\item no support for recursion
\item doesn't perform inter-procedural analysis
\item no support for JS frameworks
\item no reference to global variables and functions
\item limited support of DOM API     
\end{enumerate}

Multi-objective test suite generation. DOM reduction by means of hierarchical delta-debugging.

\subsection{Limitations}
\label{sub.sec.eval.limit}

Our framework imposes certain constraints on the structure of JS programs:

\subsection{Threats to Validity}
\label{sub.sec.thhreats}

%% --------------------------------------------------------------------
\section{Related Work}
\label{sec:related.work}
%% --------------------------------------------------------------------

There are several ways how to address the problem of input data generation for JS functions: static and dynamic analysis, symbolic execution, SBST, formal reasoning, the whole web application testing.

\subsection{Search-Based Test Case Generation}

@@

\subsection{Static and Dynamic Analysis of JavaScript}
\label{sub.sec.js.static.anal}

Static analysis is a powerful technique commonly used as solid alternative for program testing. In fact both techniques can benefit from one another. For such weakly typed and dynamic languages as JavaScript employing static analysis to infer types can be an invaluable source of information to identify potential bugs or even guarantee their absence. Jensen et al.~\cite{tajs2009} presented such an analysis for JavaScript using abstract interpretation. In the follow-up work~\cite{dom2011} they extended the analysis with the abstractions to reason about HTML DOM and browser API. Given step let the authors to carry static analysis at the level of complete web application (JavaScript + HTML).
\cite{jquery2014}

>>>>

\usepackage[inline]{enumitem}
\usepackage{tablefootnote}
\usepackage{syntax}
\usepackage{multirow}
\usepackage{multicol}
\usepackage{booktabs} % For formal tables
\usepackage{tikz}
\usetikzlibrary{arrows,shadows,positioning,decorations.pathmorphing}
\usepackage{pgf-umlsd}
\usepackage{tikz-uml}
\usepackage{hyperref}
\usepackage{upquote}
\usepackage{listings}
\usepackage{lsthaskell}
\usepackage{xspace}
\usepackage{enumitem}
\usepackage{mdframed}
\usepackage{algorithmic}
\usepackage{longtable}
\usepackage{subcaption}
\usepackage{pgfplots}
\pgfplotsset{compat=newest}
\usepackage[titlenotnumbered, linesnumbered, ruled]{algorithm2e} % language for algorithm description
\hypersetup{
  colorlinks   = true, %Colours links instead of ugly boxes
  urlcolor     = blue, %Colour for external hyperlinks
  linkcolor    = red, %Colour of internal links
  citecolor    = green %Colour of citations
}

@@

%TODO: maybe expand this section with the JS type casting for branch distance computation

@@

\subsubsection{Limitations}
\label{sub.sub.sec.limit}

Currently, our framework imposes certain explicit constraints on the kind of JS functions it is able to process: 
\begin{enumerate}
\item ability to assign static types to input parameters 
\item no support for the \emph{Object} type, heterogeneous arrays and high-order functions
\item no support for recursion
\item doesn't perform inter-procedural analysis
\item no support for JS frameworks
\item no reference to global variables and functions
\item limited support of DOM API     
\end{enumerate}

@@

%% --------------------------------------------------------------------
\section{Related and Future Work}
\label{sec:related.work}
%% --------------------------------------------------------------------

The last two decades were fruitful in the amount of work dedicates to the analysis and web applications and JavaScript, in particular. The state-of-the-art in this field including JS static and dynamic analysis, as well as test generation is captured by the two recent surveys~\cite{andreasen2017survey, sun2017analysis}. Therefore, we would like to organize our discussion of related work around two main questions: 
\begin{enumerate*}
\item test data generation for JS functions interacting with the DOM, and
\item the application of search-based techniques for that problem.
\end{enumerate*}

\subsection{Test Data Generation for JavaScript}

\emph{Jalangi}~\cite{sen2013jalangi} is a JS dynamic analysis framework which can be employed, for example, for implementing concolic testing or type inconsistency analysis~\cite{pradel2015typedevil}. It suffers from typical for the symbolic analysis problems such as the handing of arrays and loops. \emph{Confix}~\cite{amin:ase15} translates DOM-related statements into XPath expressions, and feeds them to a constrain solver in order to obtains DOM fixtures for the FUT. Combined with Jalangi it can be used for both primitive and DOM test data generation. As it has been shown early by Baars et al.~\cite{baars2011symbolic}, search-based testing can greatly benefit from symbolic analysis. Following this approach, we could try to combine \emph{JEDI} with \emph{Confix} to achieve better results.

Static analysis is a powerful technique commonly used as solid alternative for program testing. In fact both techniques can benefit from one another. For such weakly typed and dynamic languages as JavaScript employing static analysis to infer types can be an invaluable source of information to identify potential bugs or even guarantee their absence. Jensen et al.~\cite{tajs2009} presented such an analysis for JavaScript using abstract interpretation. In the follow-up work~\cite{dom2011} they extended the analysis with the abstractions to reason about HTML DOM and browser API. Given step let the authors to carry static analysis at the level of complete web application (JavaScript + HTML).

\emph{$JS_{DEP}$}~\cite{sung2016static} proposes a constraint-based static analysis for learning dependencies between DOM-events, which can help to prune the sequence of tests consisting of the web-application events.

\subsection{Search-Based Test Data Generation}

@@

\cite{jquery2014}
